\documentclass[12pt]{article}

\usepackage[left=1cm,right=1cm,
    top=2cm,bottom=2cm,bindingoffset=0cm]{geometry}
\usepackage{braket}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{mathrsfs}
\usepackage[T2A]{fontenc}
\usepackage[utf8x]{inputenc}
\usepackage[english]{babel}
\usepackage{graphicx}
\parindent=0.5cm

\usepackage{hyperref} 
\usepackage{indentfirst}

\numberwithin{equation}{section}
%\usepackage{showkeys}

\begin{document}
\section*{MSAI Statistics \& Probability – Week 2 Seminar \& HW}\\

\textbf{Problem 1:} There are $R$ red and $G$ green balls in a box. Alice and Bob pick balls from the box in turns (one ball at a time). The one who is the first to pick a red ball is the winner. Find the probability that Alice wins if she is the first to make a move and 1) they do not put balls back in the box 2) they do put them back. Write a numeric answer for $R=4$ and $G=5$.
\\

\textbf{Problem 2:} Are the following statements true?
\begin{enumerate}
    \item $p(B|A)+p(B|\bar{A})=1$
    \item $p(B|A)+p(\bar{B}|\bar{A})=1$
\end{enumerate}
\\

\textbf{Problem 3:} Two subsets, $A_1$ and $A_2$ (they may coincide) are chosen randomly from $\{1,\dots,n\}$. Find the probability that $|A_1|=l_1$ and $|A_2|=l_2$ under the condition that $A_1\cap A_2=\varnothing.$ Give a numeric answer for $n=6,~l_1=2,~l_2=3.$
\\

\textbf{Problem 4:} There are $R$ red and $G$ green balls in a box. Alice is picking balls from the box, one at a time. $A_k$ is the event that, at time $k$ ($k$-th pick), she picks a red ball. Are the events $A_1,\dots,A_n$ independent? Alice may be picking balls with replacement or without replacement – if Alice chooses to pick, say, without replacement – then she's making all the picks without replacement. Same for with replacement – provide the answer for both cases. \\
\textit{You may (or may not) need the following notion in your solution: A set of more than 2 events is called mutually (or collectively) independent, if all pairs of events in it are pairwise independent.}
\\

\textbf{Problem 5:} Every edge (independently of all others) of $K_n$ – a complete graph on $n$ vertices, is colored in one of $k$
colors. For a set of vertices $S$ of the graph, let $A_S$ be the event that all the edges having both vertices in $S$ have the same color. What are the conditions on $S,T$ for the events $A_S$ and $A_T$ to be independent?

\end{document}
