\documentclass[12pt]{article}

\usepackage[left=1cm,right=1cm,
    top=2cm,bottom=2cm,bindingoffset=0cm]{geometry}
\usepackage{braket}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{mathrsfs}
\usepackage[T2A]{fontenc}
\usepackage[utf8x]{inputenc}
\usepackage[english]{babel}
\usepackage{graphicx}
\parindent=0.5cm

\usepackage{hyperref} 
\usepackage{indentfirst}

\numberwithin{equation}{section}
%\usepackage{showkeys}

\begin{document}
\section*{MSAI Statistics \& Probability – Week 1 Seminar \& HW}\\

\textbf{Problem 1:} Two dice, each having $M$ faces, are thrown. Each die has numbers from $1$ to $M$ written on its faces. Find the probability that the sum of two numbers equals $i$. Provide the answer for $M=10,$ and $i=15.$
\\

\textbf{Problem 2:} A random subset is chosen from the set $\{1,\dots,N\}.$ Find the probability that the cardinality (number of elements) of thus subset is an even number.
\\

\textbf{Problem 3:} Two subsets, $A_1$ and $A_2,$ of $\{1,\dots,n\}$ are chosen randomly (they may coincide). Find the probability that $A_1 \cap A_2 = \emptyset$
\\

\textbf{Problem 4:} 
An algebra is a set of subsets of $\Omega$ that 1) contains $\Omega$, 2) is closed under complement (if $A$ is in the algebra – $\bar{A},$ its complement, is also) and union (if $A$ and $B$ are in the algebra – $A\cup B$ is as well). Can these two operations from point 2) be replaced with
\begin{enumerate}
    \item $\Delta$ (symmetric difference) and $\textbackslash$ (set difference, also called relative complement)?
    \item $\overline{A\cap B}$ (just one operation, complement of the intersection)?
\end{enumerate}
\\

\textbf{Problem 5:} Let $\mathcal{F}_1,~\mathcal{F}_2$ be $\sigma$-algebras. Is it true that 1) $\mathcal{F}_1\cap\mathcal{F}_2$ and 2)$\mathcal{F}_1\cup\mathcal{F}_2$ are $\sigma$-algebras?

\end{document}
